Case study validations of automatic bullet matching

### 2018-11-14 index.Rmd
add comment

\hh{
Cleanup TO-DO
\begin{itemize}
\item define false positives and false negatives once and stick to those definitions. We should avoid false positive and false negatives, because that only makes sense in a test setting, which we have not defined formally.
Let's use instead wrong identification and missed identification. 
\end{itemize}
}

@@

>>>>

\hh{
Cleanup TO-DO
\begin{itemize}
\item define false positives and false negatives once and stick to those definitions. We should avoid false positive and false negatives, because that only makes sense in a test setting, which we have not defined formally.
Let's use instead wrong identification and missed identification. 
\item error rates: we are using rates exchangeably with percentages. We need to fix that. I think percentages might be easier understood. 
\end{itemize}
}

@@

## Identification Errors
\svp{XXX define wrong identification and missed identification here XXX}
\svp{When evaluating algorithm performance, it is useful to distinguish between two types of errors, which we will refer to as \textbf{wrong identification} and \textbf{missed identification} in this paper. Wrong identifications are those in which two bullets from different sources are determined to be from the same source. Missed identifications are those in which two bullets from the same source are determined to be from different sources.}
\svp{XXX Relate to AFTE Theory of Examination criteria? How to handle ``inconclusive"?}
\svp{XXX May want to have the error type table/chart as a visual representation? XXX}
